More straightforward movement variable definitions

### 2024-04-04 scripts/01.2_categorizeMovement.qmd
re-ran with new pc's

```{r}
pca_space <- prcomp(space_use[,-c(1:3)]) # only including home range and coreAreaFidelity (because it would be redundant to include all three)
fviz_pca_biplot(pca_space, axes = c(1,2), 
                geom = c("point"), 
                alpha.ind = 0.3,
                repel = T)+
  theme_classic()
fviz_screeplot(pca_space, addLabels = T) # This is also strongly loaded on one principal component, so I feel quite comfortable taking it as a measure of roost diversification/routine
contrib_space <- round(pca_space$rotation[,1:3]*-100, 2) %>%
  as.data.frame()
contrib_space
# Multiply by -1 to flip these around, because right now `pca_space` shows these both being negatively loaded.
space_use <- space_use %>%
  mutate(space_pc1 = pca_space$x[,1]*-1)
save(pca_space, file = here("data/calcMovement/pca_space.Rda"))

# Plots of the extremes
high <- space_use %>% filter(space_pc1 == max(space_pc1, na.rm = T))
low <- space_use %>% filter(space_pc1 == min(space_pc1, na.rm = T))

```

>>>>

```{r}
pca_space <- prcomp(space_use[,-c(1:3)]) # only including home range and coreAreaFidelity (because it would be redundant to include all three)
fviz_pca_biplot(pca_space, axes = c(1,2), 
                geom = c("point"), 
                alpha.ind = 0.3,
                repel = T)+
  theme_classic()
fviz_screeplot(pca_space, addLabels = T) # This is also strongly loaded on one principal component, so I feel quite comfortable taking it as a measure of roost diversification/routine
contrib_space <- round(pca_space$rotation[,1:2]*-100, 2) %>%
  as.data.frame()
contrib_space
# Multiply by -1 to flip these around, because right now `pca_space` shows these both being negatively loaded.
space_use <- space_use %>%
  mutate(space_pc1 = pca_space$x[,1]*-1)
save(pca_space, file = here("data/calcMovement/pca_space.Rda"))
```
